### 2016-06-26 sec4_baseline.tex
A more complete one
hhah

\begin{figure*} [t]
\center
\includegraphics[width=\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Parallel Mining. (a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle uses TRPM to detect GCMP in parallel.}
\label{fig:trm}
\end{figure*}

>>>>

\begin{figure*} [t]
\center
\includegraphics[width=\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Parallel Mining (TRPM). (a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle, which uses TRPM to detect GCMP in parallel.}
\label{fig:trm}
\end{figure*}

### 2016-06-26 sec5_spm.tex
A more complete one
hhah

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\textwidth]{spm.eps}
\caption{Star partition and mining. (a) Conceptual connection graph from Figure 1.(b) Five star partitions are generated
(c) Apriori Mining with various pruning techniques.}
\label{fig:star_partition}
\end{figure*}

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\textwidth]{spm.eps}
\caption{Star partition and ApRiori Enumerator (SPARE). (a) Aggregate graph from Figure 1. (b) Five stars are generated, star IDs are circled, the vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
\end{figure*}
